Natural Language Interfaces to Structured Data

### 2012-08-10 trunk/tr-nlisurvey/src/nli-survey.tex
Standard commit Following sections have been updated: section 4: picture

% draw pictures with tikz package
\usepackage{tikz}

@@

@@

\begin{figure}
\centering
\begin{tikzpicture}

\def \n {5}
\def \radius {3cm}
\def \margin {8} % margin in angles, depends on the radius

\foreach \s in {1,...,\n}
{
  \node[draw, circle] at ({360/\n * (\s - 1)}:\radius) {$\s$};
  \draw[->, >=latex] ({360/\n * (\s - 1)+\margin}:\radius) 
    arc ({360/\n * (\s - 1)+\margin}:{360/\n * (\s)-\margin}:\radius);
}
\end{tikzpicture}
\caption{Big picture of NLI systems}
\label{fig:big-picture}
\end{figure}

>>>>

% draw pictures with tikz package
\usepackage{tikz}
\usetikzlibrary{arrows, petri, topaths}
\usepackage{tkz-berge}

@@

\begin{figure*}
\centering
\begin{tikzpicture}[transform shape]
%\tikzset{VertexStyle/.append style = {minimum size = 3pt}}
\node at (0,0) [draw,circle,inner sep=2pt](1){1};
\node at (3,0) [draw,circle,inner sep=2pt](2){2};
\node at (7,0) [draw,circle,inner sep=2pt](3){3};
\node at (10,0) [draw,circle,inner sep=2pt](4){4};
\node at (14,0) [draw,circle,inner sep=2pt](5){5};
\node at (0,0) [draw=none,fill=none,label={[label distance=3pt]0:{NL query}}]
{}; 
\node at (3,0) [draw=none,fill=none,label={[label
distance=3pt]0:{intermediate query}}] {}; 
\node at (7,0) [draw=none,fill=none,label={[label
distance=3pt]0:{query graph}}] {};
\node at (10,0) [draw=none,fill=none,label={[label
distance=3pt]0:{logic query graph}}] {};
\node at (14,0) [draw=none,fill=none,label={[label
distance=3pt]0:{database query}}] {};
\draw[->](1) edge[bend left] (2);
\draw[->](2) edge[bend left] (3);
\draw[->](3) edge[bend left] (4);
\draw[->](4) edge[bend left] (5);
\end{tikzpicture}
\caption{Big picture of NLI systems}
\label{fig:big-picture}
\end{figure*}

@@
